Conservation of interaction partners between related plants varies widely across communities and between plant families - Supporting Information

### 2019-02-20 manuscript/supporting_info.tex
supporting info now all pretty

\section*{Supporting information 1: Sources for networks}

  \begin{table}[!h]
    \caption{Original sources for each network used in our analyses.}
    \label{sources}
    \begin{tabular}{|l l l |}
    \hline
    Network & Network type & Original source \\
    \hline
    M\_PL\_001  & Pollination & \citep{Arroyo1982}  \\
    M\_PL\_002  & Pollination & \citep{Arroyo1982}  \\
    M\_PL\_003  & Pollination & \citep{Arroyo1982}  \\
    M\_PL\_004  & Pollination & \citep{Barrett1987} \\
    M\_PL\_005  & Pollination & \citep{Clements1923}  \\
    M\_PL\_006  & Pollination & \citep{Dicks2002} \\
    M\_PL\_007  & Pollination & \citep{Dicks2002} \\
    M\_PL\_008  & Pollination & \citep{Dupont2003}  \\
    M\_PL\_009  & Pollination & \citep{Elberling1999} \\
    M\_PL\_010  & Pollination & Elberling, H. \& Olesen, J. M. Unpublished. \\
    M\_PL\_011  & Pollination & \citep{Olesen2002a}  \\
    M\_PL\_012  & Pollination & Olesen, J. M. Unpublished.  \\
    M\_PL\_013  & Pollination & \citep{Ollerton2003}  \\
    M\_PL\_014  & Pollination & \citep{Hocking1968} \\
    M\_PL\_015  & Pollination & \citep{Petanidou1991} \\
    M\_PL\_016  & Pollination & \citep{Herrera1988} \\
    M\_PL\_017  & Pollination & \citep{Memmott1999} \\
    M\_PL\_018  & Pollination & Olesen, J. M. Unpublished.  \\
    M\_PL\_019  & Pollination & \citep{Inouye1988}  \\
    M\_PL\_020  & Pollination & \citep{Kevan1970} \\
    M\_PL\_021  & Pollination & \citep{Kato1999}  \\
    M\_PL\_022  & Pollination & \citep{Medan2002} \\
    M\_PL\_023  & Pollination & \citep{Medan2002} \\
    M\_PL\_024  & Pollination & \citep{Mosquin1967} \\
    M\_PL\_025  & Pollination & \citep{Motten1982}  \\
    M\_PL\_026  & Pollination & \citep{McMullen1993}  \\
    M\_PL\_027  & Pollination & \citep{Primack1983} \\
    M\_PL\_028  & Pollination & \citep{Primack1983} \\
    M\_PL\_029  & Pollination & \citep{Primack1983} \\
    M\_PL\_030  & Pollination & \citep{Ramirez1992} \\
    M\_PL\_031  & Pollination & \citep{Ramirez1989} \\
    M\_PL\_032  & Pollination & \citep{Schemske1978}  \\
    M\_PL\_033  & Pollination & \citep{Small1976} \\
    M\_PL\_034  & Pollination & \citep{SmithRamirez2005}  \\
    M\_PL\_035  & Pollination & \citep{Percival1974}  \\
    M\_PL\_036  & Pollination & Olesen, J. M. Unpublished.  \\
    \hline
    \end{tabular}

@@

    \begin{tabular}{|l l l |}
    \hline
    Network & Network type & Original source \\
    \hline
    M\_PL\_037  & Pollination & \citep{Montero2005} \\
    M\_PL\_038  & Pollination & \citep{Montero2005} \\
    M\_PL\_039  & Pollination & \citep{Stald2003} \\
    M\_PL\_040  & Pollination & \citep{Ingversen2006} \\
    M\_PL\_041  & Pollination & \citep{Ingversen2006} \\
    M\_PL\_042  & Pollination & \citep{Philipp2006} \\
    M\_PL\_043  & Pollination & \citep{Montero2005} \\
    M\_PL\_044  & Pollination & \citep{Kato2000}  \\
    M\_PL\_045  & Pollination & \citep{Lundgren2005}  \\
    M\_PL\_046  & Pollination & \citep{Bundgaard2003} \\
    M\_PL\_047  & Pollination & \citep{Dupont2009a}  \\
    M\_PL\_048  & Pollination & \citep{Dupont2009a}  \\
    M\_PL\_049  & Pollination & \citep{Beks2006}  \\
    M\_PL\_050  & Pollination & \citep{Stald2003} \\
    M\_PL\_051  & Pollination & \citep{Vazquez2002} \\
    M\_PL\_052  & Pollination & \citep{Witt1998}  \\
    M\_PL\_053  & Pollination & \citep{Yamazaki2003}  \\
    M\_PL\_054  & Pollination & \citep{Kakutani1990}  \\
    M\_PL\_055  & Pollination & \citep{Kato1996}  \\
    M\_PL\_056  & Pollination & \citep{Kato1993}  \\
    M\_PL\_057  & Pollination & \citep{Inoue1990} \\
    M\_PL\_058  & Pollination & \citep{Bartomeus2008} \\
    M\_PL\_059  & Pollination & \citep{Bezerra2009} \\
    Basset  & Herbivory & \citep{Basset1999}  \\
    Bluthgen  & Herbivory & \citep{Bluthgen2006}  \\
    Bodner  & Herbivory & \citep{Bodner2010}  \\
    Coley & Herbivory & \citep{Coley2006} \\
    Ibanez  & Herbivory & \citep{Ibanez2013}  \\
    Joern\_altuda  & Herbivory & \citep{Joern1979} \\
    Joern\_marathon  & Herbivory & \citep{Joern1979} \\
    Novotny & Herbivory & \citep{Novotny2012} \\
    Peralta & Herbivory & \citep{Peralta2015} \\
    Sheldon & Herbivory & \citep{Sheldon1978} \\
    Ueckert & Herbivory & \citep{Ueckert1971} \\
    \hline
    \end{tabular}
    \end{table}

@@

% \begin{figure}[!h]
%     \begin{center}
%       \centerline{\includegraphics*[height=.62\textheight]{Figures/random_p_distributions.eps}}
%     \end{center}
%      \caption{Distributions of $p$-values obtained when comparing the strength of the relationship between niche overlap and phylogenetic distance in 999 permutations of each network in our dataset with 500 permutations of each permuted network. Each line in each panel represents the histogram of $p$-values for one network. Bins are 0.05 wide. Purple lines in panels A-L represent pollination networks while green lines in panels M-N represent plant-herbivore networks. Networks are as follows (darkest to lightest):
%      \textbf{A)} M_PL_001, M_PL_002, M_PL_003, M_PL_004, M_PL_005;
%      \textbf{B)} M_PL_006, M_PL_007, M_PL_008, M_PL_009, M_PL_010;
%      \textbf{C)} M_PL_011, M_PL_012, M_PL_013, M_PL_014, M_PL_015;
%      \textbf{D)} M_PL_016, M_PL_017, M_PL_018, M_PL_019, M_PL_020;
%      \textbf{E)} M_PL_021, M_PL_022, M_PL_023, M_PL_024, M_PL_025;
%      \textbf{F)} M_PL_026, M_PL_027, M_PL_028, M_PL_029, M_PL_030;
%      \textbf{G)} M_PL_031, M_PL_032, M_PL_033, M_PL_034, M_PL_035;
%      \textbf{H)} M_PL_036, M_PL_037, M_PL_038, M_PL_039, M_PL_040;     
%      \textbf{I)} M_PL_041, M_PL_042, M_PL_043, M_PL_044, M_PL_045;
%      \textbf{J)} M_PL_046, M_PL_047, M_PL_048, M_PL_049, M_PL_050;     
%      \textbf{K)} M_PL_051, M_PL_052, M_PL_053, M_PL_054, M_PL_055;
%      \textbf{L)} M_PL_056, M_PL_057, M_PL_058, M_PL_059;
%      \textbf{M)} Ibanez, Joern_altuda, Joern_marathon, Peralta, Sheldon;
%      \textbf{N)} Ueckert, Basset, Bluthgen, Bodner, Coley, Novotny.
%      For original sources for each network, see Table S1.
%      }
%     \label{within_family_regression}
%   \end{figure}

>>>>

\beginsupplement
\clearpage

\section*{Supporting information 1: Sources for networks}
  \begin{table}[!h]
    \caption{Original sources for each network used in our analyses.}
    \label{sources}
    \begin{center}
    \begin{tabular}{|l l m{6cm} |}
    \hline
    Network & Network type & Original source \\
    \hline
    M\_PL\_001  & Pollination & \citep{Arroyo1982}  \\
    M\_PL\_002  & Pollination & \citep{Arroyo1982}  \\
    M\_PL\_003  & Pollination & \citep{Arroyo1982}  \\
    M\_PL\_004  & Pollination & \citep{Barrett1987} \\
    M\_PL\_005  & Pollination & \citep{Clements1923}  \\
    M\_PL\_006  & Pollination & \citep{Dicks2002} \\
    M\_PL\_007  & Pollination & \citep{Dicks2002} \\
    M\_PL\_008  & Pollination & \citep{Dupont2003}  \\
    M\_PL\_009  & Pollination & \citep{Elberling1999} \\
    M\_PL\_010  & Pollination & Elberling, H. \& Olesen, J. M. Unpublished. \\
    M\_PL\_011  & Pollination & \citep{Olesen2002a}  \\
    M\_PL\_012  & Pollination & Olesen, J. M. Unpublished.  \\
    M\_PL\_013  & Pollination & \citep{Ollerton2003}  \\
    M\_PL\_014  & Pollination & \citep{Hocking1968} \\
    M\_PL\_015  & Pollination & \citep{Petanidou1991} \\
    M\_PL\_016  & Pollination & \citep{Herrera1988} \\
    M\_PL\_017  & Pollination & \citep{Memmott1999} \\
    M\_PL\_018  & Pollination & Olesen, J. M. Unpublished.  \\
    M\_PL\_019  & Pollination & \citep{Inouye1988}  \\
    M\_PL\_020  & Pollination & \citep{Kevan1970} \\
    M\_PL\_021  & Pollination & \citep{Kato1999}  \\
    M\_PL\_022  & Pollination & \citep{Medan2002} \\
    M\_PL\_023  & Pollination & \citep{Medan2002} \\
    M\_PL\_024  & Pollination & \citep{Mosquin1967} \\
    M\_PL\_025  & Pollination & \citep{Motten1982}  \\
    M\_PL\_026  & Pollination & \citep{McMullen1993}  \\
    M\_PL\_027  & Pollination & \citep{Primack1983} \\
    M\_PL\_028  & Pollination & \citep{Primack1983} \\
    M\_PL\_029  & Pollination & \citep{Primack1983} \\
    M\_PL\_030  & Pollination & \citep{Ramirez1992} \\
    M\_PL\_031  & Pollination & \citep{Ramirez1989} \\
    \hline
    \end{tabular}
    \end{center}
    \end{table}

@@

    \begin{table*}[h!]
    \begin{center}
    \begin{tabular}{|l l m{6cm} |}
    \hline
    Network & Network type & Original source \\
    \hline
    M\_PL\_032  & Pollination & \citep{Schemske1978}  \\
    M\_PL\_033  & Pollination & \citep{Small1976} \\
    M\_PL\_034  & Pollination & \citep{SmithRamirez2005}  \\
    M\_PL\_035  & Pollination & \citep{Percival1974}  \\
    M\_PL\_036  & Pollination & Olesen, J. M. Unpublished.  \\
    M\_PL\_037  & Pollination & \citep{Montero2005} \\
    M\_PL\_038  & Pollination & \citep{Montero2005} \\
    M\_PL\_039  & Pollination & \citep{Stald2003} \\
    M\_PL\_040  & Pollination & \citep{Ingversen2006} \\
    M\_PL\_041  & Pollination & \citep{Ingversen2006} \\
    M\_PL\_042  & Pollination & \citep{Philipp2006} \\
    M\_PL\_043  & Pollination & \citep{Montero2005} \\
    M\_PL\_044  & Pollination & \citep{Kato2000}  \\
    M\_PL\_045  & Pollination & \citep{Lundgren2005}  \\
    M\_PL\_046  & Pollination & \citep{Bundgaard2003} \\
    M\_PL\_047  & Pollination & \citep{Dupont2009a}  \\
    M\_PL\_048  & Pollination & \citep{Dupont2009a}  \\
    M\_PL\_049  & Pollination & \citep{Beks2006}  \\
    M\_PL\_050  & Pollination & \citep{Stald2003} \\
    M\_PL\_051  & Pollination & \citep{Vazquez2002} \\
    M\_PL\_052  & Pollination & \citep{Witt1998}  \\
    M\_PL\_053  & Pollination & \citep{Yamazaki2003}  \\
    M\_PL\_054  & Pollination & \citep{Kakutani1990}  \\
    M\_PL\_055  & Pollination & \citep{Kato1996}  \\
    M\_PL\_056  & Pollination & \citep{Kato1993}  \\
    M\_PL\_057  & Pollination & \citep{Inoue1990} \\
    M\_PL\_058  & Pollination & \citep{Bartomeus2008} \\
    M\_PL\_059  & Pollination & \citep{Bezerra2009} \\
    Basset  & Herbivory & \citep{Basset1999}  \\
    Bluthgen  & Herbivory & \citep{Bluthgen2006}  \\
    Bodner  & Herbivory & \citep{Bodner2010}  \\
    Coley & Herbivory & \citep{Coley2006} \\
    Ibanez  & Herbivory & \citep{Ibanez2013}  \\
    Joern\_altuda  & Herbivory & \citep{Joern1979} \\
    Joern\_marathon  & Herbivory & \citep{Joern1979} \\
    Novotny & Herbivory & \citep{Novotny2012} \\
    Peralta & Herbivory & \citep{Peralta2015} \\
    Sheldon & Herbivory & \citep{Sheldon1978} \\
    Ueckert & Herbivory & \citep{Ueckert1971} \\
    \hline
    \end{tabular}
    \end{center}
    \end{table*}
\clearpage
\newpage

@@

\begin{figure}[!h]
    \begin{center}
      \centerline{\includegraphics*[width=.75\textwidth]{Figures/random_p_distributions.eps}}
    \end{center}
     \caption{\small Distributions of $p$-values obtained when comparing the strength of the relationship between niche overlap and phylogenetic distance in 999 permutations of each network in our dataset with 500 permutations of each permuted network. Each line in each panel represents the histogram of $p$-values for one network. Bins are 0.05 wide. Purple lines in panels A-L represent pollination networks while green lines in panels M-N represent plant-herbivore networks. A list of networks shown on each panel follows; see Table S1 for original sources.
     % Networks are as follows (darkest to lightest): \textbf{A)} M\_PL\_001, M\_PL\_002, M\_PL\_003, M\_PL\_004, M\_PL\_005;      \textbf{B)} M\_PL\_006, M\_PL\_007, M\_PL\_008, M\_PL\_009, M\_PL\_010;      \textbf{C)} M\_PL\_011, M\_PL\_012, M\_PL\_013, M\_PL\_014, M\_PL\_015;      \textbf{D)} M\_PL\_016, M\_PL\_017, M\_PL\_018, M\_PL\_019, M\_PL\_020;      \textbf{E)} M\_PL\_021, M\_PL\_022, M\_PL\_023, M\_PL\_024, M\_PL\_025;   \textbf{F)} M\_PL\_026, M\_PL\_027, M\_PL\_028, M\_PL\_029, M\_PL\_030;     \textbf{G)} M\_PL\_031, M\_PL\_032, M\_PL\_033, M\_PL\_034, M\_PL\_035;   \textbf{H)} M\_PL\_036, M\_PL\_037, M\_PL\_038, M\_PL\_039, M\_PL\_040;     \textbf{I)} M\_PL\_041, M\_PL\_042, M\_PL\_043, M\_PL\_044, M\_PL\_045; \textbf{J)} M\_PL\_046, M\_PL\_047, M\_PL\_048, M\_PL\_049, M\_PL\_050;      \textbf{K)} M\_PL\_051, M\_PL\_052, M\_PL\_053, M\_PL\_054, M\_PL\_055;     \textbf{L)} M\_PL\_056, M\_PL\_057, M\_PL\_058, M\_PL\_059;      \textbf{M)} Ibanez, Joern\_altuda, Joern\_marathon, Peralta, Sheldon;      \textbf{N)} Ueckert, Basset, Bluthgen, Bodner, Coley, Novotny.     For original sources for each network, see Table S1.
     }
    \label{within_family_regression}
  \end{figure}

\subsection*{Networks shown in each panel of Figure S1}

All names are as in Table S1. Networks included in each panel (from darkest to lightest line colours) are:

\noindent \textbf{A)} M\_PL\_001, M\_PL\_002, M\_PL\_003, M\_PL\_004, M\_PL\_005;      \\
\textbf{B)} M\_PL\_006, M\_PL\_007, M\_PL\_008, M\_PL\_009, M\_PL\_010;    \\
\textbf{C)} M\_PL\_011, M\_PL\_012, M\_PL\_013, M\_PL\_014, M\_PL\_015;  \\
\textbf{D)} M\_PL\_016, M\_PL\_017, M\_PL\_018, M\_PL\_019, M\_PL\_020;   \\
\textbf{E)} M\_PL\_021, M\_PL\_022, M\_PL\_023, M\_PL\_024, M\_PL\_025;  \\
\textbf{F)} M\_PL\_026, M\_PL\_027, M\_PL\_028, M\_PL\_029, M\_PL\_030;  \\
\textbf{G)} M\_PL\_031, M\_PL\_032, M\_PL\_033, M\_PL\_034, M\_PL\_035; \\
\textbf{H)} M\_PL\_036, M\_PL\_037, M\_PL\_038, M\_PL\_039, M\_PL\_040;   \\
\textbf{I)} M\_PL\_041, M\_PL\_042, M\_PL\_043, M\_PL\_044, M\_PL\_045;\\
\textbf{J)} M\_PL\_046, M\_PL\_047, M\_PL\_048, M\_PL\_049, M\_PL\_050;  \\
\textbf{K)} M\_PL\_051, M\_PL\_052, M\_PL\_053, M\_PL\_054, M\_PL\_055;   \\
\textbf{L)} M\_PL\_056, M\_PL\_057, M\_PL\_058, M\_PL\_059;  \\
\textbf{M)} Ibanez, Joern\_altuda, Joern\_marathon, Peralta, Sheldon;  \\
\textbf{N)} Ueckert, Basset, Bluthgen, Bodner, Coley, Novotny.
